---
title: "Assignment 3: Air Quality Risk Assessment"
author: "Grace Bryan & Elena Nirgiotis"
date: "May 13, 2026"
format: pdf
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## **Overview**

text

## **Load Packages**

```{r}

```

## **Part 1: Build the Dataset**

```{r}

```

### **Why We Chose This Distribution**

text

### **Create the Dataset**

```{r}

```

## **Part 2: Classify Risk with a For Loop**

### **Risk Classification Rules**

- **good:** PM2.5 below 12 µg/m³
- **moderate:** PM2.5 between 12 and 35.4 µg/m³
- **unhealthy:** PM2.5 above 35.4 µg/m³

### **Use a For Loop to Fill Risk Column**

```{r}

```

## **Part 3: Seasonal Summary with a For Loop**

### **Count Unhealthy Days by Season**

```{r}

```

### **Convert Seasonal Summary to Data Frame**

```{r}

```

## **Part 4: Visualize and Report**

### **Plot 1: PM2.5 Across the Year**

```{r}

```

### **Plot 2: Count of Risk Categories**

```{r}

```

## **Management Summary**

text
